Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-27 Scripts/Initial_Analysis.Rmd
Included figure with connections

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo",
  "parallel" # for mclapply
)

@@

@@

## Functions and Data needed

### Fun `SummaryProp`

@@

  SummaryProp <- function(taxon_key){

@@

    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

### Fun `EEZProp`

@@

EEZProp <- function(taxon_list){

 spp <- bind_rows(
   lapply(taxon_list,SummaryProp)
   )

@@

### Fun `PropChange`

@@

PropChange <- function(taxon_list){

 eez <- EEZProp(taxon_list)

@@

## Run Results Analysis

@@

results <- PropChange(taxon_list)

# write_csv(Results,
#           "Clean_Results.csv")

clean_results <- fread(paste(result_path,"Clean_Results.csv",sep=""))
View(clean_results)

@@

## Figure 1. Change Map

```{r figure_one, eval = T, echo =F}

# The path
path_world <- paste(data_path,"Spatial_Data/SAU_Shapefile/",sep="")

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name)

# View(unique(World_sf$eez_name))

@@

>>>>

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo",
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot" # for Juanito's map
)

@@

ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(5,"line")
  )
}

@@

## Percentage Change

This results only shows the average percentage change in proportion of all speecies within an EEZ without relationship with neighbours

### Functions and Data needed

#### Fun `SummaryProp`

@@

SummaryProp <- function(taxon_key,links="NA"){

@@

  if(links == "y"){
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )
    }

@@

#### Fun `EEZProp`

@@

EEZProp <- function(taxon_list,links="NA"){

 spp <- bind_rows(
   lapply(taxon_list,SummaryProp,links)
   )

 if(links == "y"){

   eez_summary <- spp %>% 
     group_by(eez_name,eez_neighbour,time_step) %>% 
     summarise(
       n_spp = n(),
       min_spp = min(mean_spp,na.rm=T),
       max_spp = max(mean_spp,na.rm=T),
       sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_spp = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_spp,mean_spp,sd_spp)

 }else{

@@

#### Fun `PropChange`

@@

PropChange <- function(taxon_list,links="NA"){

 eez <- EEZProp(taxon_list,links)

@@

### Run Results Analysis

@@

# Run results
results <- PropChange(taxon_list, links="y") %>% 
  mutate(per_mid =ifelse(per_mid >= 25, 25,
                           ifelse(per_mid <= -25,-25,per_mid)
                           )
         )

# View(results)

### Load Data

# The path
path_world <- paste(data_path,"Spatial/SAU_Shapefile/",sep="")

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

# Call world map from natural earth
world_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf"))

@@

### Fig.Percentage Change Map

```{r fig_map_per, eval = F, echo =F}

World_sf %>% 
  left_join(results,
            by = "eez_name") %>% 
  filter(variable %in% c("mean_spp")#,
         # eez_name %in% c("Peru","Chile","Ecuador","Argentina")
         ) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = per_mid
    )
  ) + 
  geom_sf(data=country10_sf) +
  scale_fill_gradient2("Average Change in\nStock-Share Ratio (%)\nBy Mid Century") +
  ggtheme_map() +
  ggsave("figure_one.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

### Fig. Netowrk

```{r fig_map_Juan, eval = F, echo =F}

# Figure made thanks to Juanito!
# http://jsmayorga.com/post/mapping-the-global-network-of-transnational-fisheries/

# Get the center poligon of each EEZ for map source/target
coords <- as.data.frame(st_centroid(World_eez_sf)) %>% 
  ungroup() %>% 
  select(eez_name,geometry) %>% 
  separate(col = geometry, into = c("longitude", "latitude"), sep = "\\,")

# Remove "c()"
coords$longitude <- gsub("\\(","",coords$longitude)
coords$longitude <- gsub("c","",coords$longitude)
coords$latitude <- gsub(")","",coords$latitude)

coords <- coords %>% 
  mutate_at(vars(longitude,latitude),as.numeric)

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(coords,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(coords,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>% 
  filter(per_mid > 0,
         variable == "mean_spp"#,
         # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326)

#  unpack the coordinates of each feature 
coord_data <- as.data.frame( st_coordinates(st_cast(network_data_sf,"MULTILINESTRING")$geometry))

c(network_data_sf$line_id, network_data_sf$coords) %<-% (
  coord_data %>% 
    rename(subline_id = L1) %>%   
    nest(-L2)
)

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2)

# Plot it!

x <- ggplot() +
  geom_sf(data = world_map, size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  # geom_point(data = Data,
  #            aes(start_lon,
  #                start_lat,
  #                col = per_mid),
  #            size = 0.1,
  #            col = "black",
  #            # shape = 21,
  #            stroke = 1.5) +
  geom_path(data = paths,
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc")),
            show.legend = NA) +
  # geom_sf_text(data =World_eez_sf, aes(label =eez_name),
  #              size = 2) +
  # geom_text_repel(data = paths,
  #                  aes(
  #                    x = X,
  #                    y = Y,
  #                    label =source),
  #                  force = 1
  # )+
  ggtheme_map() +
  scale_colour_gradientn("Gain of Stock-Share Ratio (%)",
                         colours = wesanderson::wes_palette("Zissou1", 100, type = "continuous"),
                         limits = c(0,25),
                         breaks = seq(0,25,5)
  )+ 
  ggsave("figure_connections.png",
       width = 10,
       height = 6,
       units = "in"
)
